---
title: "Introduction to PhenoPath"
author: "Kieran R Campbell"
date: "2017-6-6"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Example on simulated data

```{r simulate-data, eval = FALSE}
set.seed(123L)
devtools::load_all("~/oxford/phenopath/")
sim <- simulate_phenopath()
```

See results:

```{r see-results, eval = FALSE}
fit <- phenopath(sim$y, sim$x, z_init = sim$z,elbo_tol = 1e-7)
```

plot results

```{r plot-results, eval = FALSE}
plot(sim$z, fit$m_z)
cor(sim$z, fit$m_z)
```

0.9980693

PCA

```{r sim-pca, eval = F}
sim <- simulate_phenopath(N = 200, 
                          G_de = 0, G_pst = 100, G_pst_beta = 10,
                          G_de_pst_beta = 10)

pca_df <- as_data_frame(prcomp(sim$y)$x[,1:2]) %>% 
  mutate(z = sim[['z']], x = sim[['x']])

ggplot(pca_df, aes(x = PC1, y = PC2, color = z)) +
  geom_point() 

ggplot(pca_df, aes(x = PC1, y = PC2, color = factor(x))) +
  geom_point() 
```

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
